---
title: "hw4"
output: html_document
---

```{r setup, include=FALSE}
library(datasets)
library(dplyr)
library(ggplot2)

```

## Q1
```{r}
weight0 <- ChickWeight %>%
  group_by(Diet) %>%
  summarize(avg = mean(weight), sd= sd(weight))
  
print(weight0)
```

## Q2
```{r}
complete <- ChickWeight %>%
  group_by(Chick) %>%
  mutate(num_measurements=n()) %>%
  filter(num_measurements >= 12)

print(head(complete,3))
```

## Q3
```{r}
complete <- complete %>% 
  mutate(weightgain = weight - weight[Time == 0.0])

print(head(complete, 3))
```

## Q4
```{r}
diets <- complete %>% filter(Time == 21)
plot <- ggplot(diets, aes(x=reorder(Diet, weightgain, FUN = median), y=weightgain)) + geom_boxplot()
plot <- plot + expand_limits(y=0)
print(plot) 
```

The weight gain varied heavily between the 4 different diets. The diet which resulted in the most weight gain was diet 3, with a median weight gain of almost 250. Diet 4 had a median of almost 200, diet 2 175, and diet 1 125. However, diet 4 looks to be a bit more consistent, with no chicks having a weight gain less than 150. With diet 3, the median was higher, but there is a wide range and some chicks almost had a weight gain as low as 100. 

## Q5
```{r}
arranged <- diets %>% arrange(weightgain)
print(tail(arranged, 1)) ## most gained
print(head(arranged, 1)) ## least gained

plot <- diets %>%
  ggplot(aes(x = Chick, y = weightgain, shape = Diet, color = Diet)) + geom_point()

print(plot)
```

Chick 35 gained the most, and was on diet 3. Chick 24 gained the least and was on diet 2. 

## Q6
